Rapid technological progress in white light-emitting diodes \\ and its sources in innovation and technology spillovers

### 2024-03-23 2_SSL_NE/article/article_supplementary.tex
in the middle of issues with supplement toc

% custom section designations
% https://tex.stackexchange.com/a/712523
\titleformat{\section}[display]{\large\bfseries\filright}{\bfseries Supplementary Note \thesection}{-5pt}{}
\crefname{section}{Supplementary Note}{Supplementary Notes}
% custom equation designations
\renewcommand{\figurename}{Supplementary Figure}
\crefname{figure}{Supplementary Figure}{Supplementary Figures}
\renewcommand{\tablename}{Supplementary Table}
\crefname{table}{Supplementary Table}{Supplementary Tables}

@@

\clearpage
\section{Previous Literature on Technological Progress in LEDs}
\label{sec:prev_lit}

@@

\begin{itemize}
    \item Publications often look only at progress across a select few LED device sub-efficiencies, often during a very short time period and, most importantly, only at devices manufactured by one specific company, e.g., OSRAM Opto Semiconductors in \cite{hahn2014development} or Lumileds in \cite{Bhardwaj2017}.
    \item Publications do not report on a number of potentially sensitive or proprietary advances, especially following the market entry of Chinese LED manufacturing companies as a result of the 12th Five-Year Plan (cf. \cite{guo2017china}).
    \item Publications typically do not look at the overall LED efficiency and its underlying physical limits and tend to overlook the metrics of progress related to consumer experience. 
\end{itemize}

@@

\clearpage
\section{Metrics for Technological Progress in LEDs}

\textbf{Motivation for Methods Selection}

@@

\section{Background of Interviewed Experts}

\clearpage
\section{Metrics: Device Performance}
\label{sec:device_performance_metrics}

@@

\clearpage
\section{Metrics: Consumer Experience}
\label{sec:metrics_consumer}

@@

\clearpage
\section{Methods: Cost Model Structure}
\label{sec:costmodel_structure}

@@

\clearpage
\section{Methods: Cost Model Limitations}
\label{sec:costmodel_limitations}

@@

\section{Diagrams: Chip Architecture Manufacturing Process Steps}
\label{sec:manufacturing_steps}

\section{Cost Model: Computation of Yielded Cost}
\label{sec:cost_computation}

@@

\section{Cost Model: Contribution of Variables}
\label{sec:contribution_variables}

@@

\newpage
\section{Cost Model: Sensitivity Analysis}

@@

\clearpage
\section{Cost Model: Comparison with Industry Data/Projections}
\label{sec:cost_model_calibration}

@@

\clearpage
\section{Historical Progress in Sub-Efficiencies}

Empirical data on the historical progress in metrics related to four different sub-efficiencies contributing to the overall LED efficiency (lamp efficiency $\eta_L$) is shown in \cref{fgr:subeff}:

\begin{figure}[H]
\centering
\includegraphics[width=15.5cm]{./figures/subefficiencies_progress.pdf}
\caption{\textbf{Historical improvements in LED sub-efficiencies.} Panels A1-A2 show data for key metrics used to calculate forward voltage efficiency $\eta_{Vf}$ and droop efficiency $\eta_{droop}$. Panels B1-B2 show data for internal quantum efficiency $\eta_{IQ}$ and light extraction efficiency $\eta_{LE}$. Source: own synthesis of data from the list of sources provided in \cref{sec:sources}. Data on average device performance adapted from U.S. Department of Energy (DOE) Reports \cite{doe_ssl_multiyear_2007}\cite{doe_ssl_multiyear_2008}\cite{doe_ssl_multiyear_2013}\cite{doe_ssl_rnd_2016}\cite{doe_ssl_rnd_2018} and an Osram company report \cite{beale_leds_2015}.}
\label{fgr:subeff}
\vspace{-20mm}
\end{figure}

\clearpage
\section{Non-Phosphor-Related LED Innovations}

\clearpage
\section{Phosphor-Related LED Innovations}
\label{sec:innovation_phosphor}

\section{Spectral Data for Phosphors}

\clearpage
\section{Full List of Sources for Figures}
\label{sec:sources}

\newpage

\printbibliography[title=Supplementary References]

>>>>

% custom section designations
% https://tex.stackexchange.com/a/712523

\newcounter{suppnotecounter}
\newcommand{\suppnote}[1]{%
  \stepcounter{suppnotecounter}%
  \subsection*{\large\bfseries\filright Supplementary Note \arabic{suppnotecounter}: \\ #1}%
  \addcontentsline{toc}{subsection}{#1}%
  \label{suppnote:#1}
}

\newcounter{suppdisccounter}
\newcommand{\suppdisc}[1]{%
  \stepcounter{suppdisccounter}%
  \subsection*{\large\bfseries\filright Supplementary Discussion \arabic{suppdisccounter}: \\ #1}%
  \addcontentsline{toc}{subsection}{#1}%
}

\newcounter{suppmethcounter}
\newcommand{\suppmeth}[1]{%
  \stepcounter{suppmethcounter}%
  \subsection*{\large\bfseries\filright Supplementary Method \arabic{suppmethcounter}: \\ #1}%
  \addcontentsline{toc}{subsection}{#1}%
}

\newcounter{supprefcounter}
\newcommand{\suppref}[1]{%
  \stepcounter{supprefcounter}%
  \subsection*{\large\bfseries\filright Supplementary References \arabic{supprefcounter}: \\ #1}%
  \addcontentsline{toc}{subsection}{#1}%
}

% custom equation designations
\renewcommand{\figurename}{Supplementary Figure}
\crefname{figure}{Supplementary Figure}{Supplementary Figures}
\renewcommand{\tablename}{Supplementary Table}
\crefname{table}{Supplementary Table}{Supplementary Tables}

@@

\addcontentsline{toc}{section}{Supplementary Notes}

\suppnote{Previous Literature on Technological Progress in LEDs}
\label{sec:prev_lit}

\cref{sec:prev_lit}

@@

Publications often look only at progress across a select few LED device sub-efficiencies, often during a very short time period and, most importantly, only at devices manufactured by one specific company, e.g., OSRAM Opto Semiconductors in \cite{hahn2014development} or Lumileds in \cite{Bhardwaj2017}. Publications do not report on a number of potentially sensitive or proprietary advances, especially following the market entry of Chinese LED manufacturing companies as a result of the 12th Five-Year Plan (cf. \cite{guo2017china}). Publications typically do not look at the overall LED efficiency and its underlying physical limits and tend to overlook the metrics of progress related to consumer experience.

@@

\suppnote{Manufacturing Process Steps}
\label{sec:manufacturing_steps}

\suppnote{Historical Progress in Chip Architectures}
\label{sec:chip_architecture}

\begin{figure}[h!]
\centering
\includegraphics[height=15cm]{figures/chip_architecture_overview.pdf}
\caption{\textbf{Historical evolution of LED chip architectures.} Panel A: classical chip with lateral current spreading; Panel B: Osram’s thin GaN flip-chip (vertical) architecture; Panel C: flip-chip architecture; Panel D: chip-scale package flip-chip architecture. Shown are side views of chips without packages, along a cutaway line best suited to the features of each architecture. The cutaway surface is indicated by a red arrow with an eye on the overlaid top view of each chip. Note that the dimensions are not to scale, and smaller features are greatly exaggerated for clarity. Years indicated correspond to the earliest identified patent priority date. Black frames around certain designs indicate chip designs not brought to large-scale production. Chip architecture abbreviations: TF - Thin-Film; FC - Flip-Chip; CSP - Chip-Scale Package; Material abbreviations: GaN - Gallium Nitride, ITO - Indium Tin Oxide, MQW - Multiple Quantum Well. Source: adapted and compiled from multiple patents and industry publications. See Supplementary Note 16 for the full list of sources and references.}
\label{fgr:chip_architecture_overview}
\end{figure}

We summarize the information collected and analysed on the progress in GaN-based LED chip architectures and manufacturing processes in \cref{fgr:chip_architecture_overview}, where we show the evolution of LEDs from classical chips with lateral current spreading to chip-scale package flip-chip architectures. We use this information as input into LED performance calculations and manufacturing cost modeling.

\clearpage
\suppnote{Historical Progress in Sub-Efficiencies}
\label{sec:subeff_progress}

\begin{figure}[H]
\centering
\includegraphics[width=15.5cm]{./figures/subefficiencies_progress.pdf}
\caption{\textbf{Historical improvements in LED sub-efficiencies.} Panels A1-A2 show data for key metrics used to calculate forward voltage efficiency $\eta_{Vf}$ and droop efficiency $\eta_{droop}$. Panels B1-B2 show data for internal quantum efficiency $\eta_{IQ}$ and light extraction efficiency $\eta_{LE}$. Source: own synthesis of data from the list of sources provided in \cref{sec:sources}. For an illustration of the different chip architectures shown, compare \cref{sec:chip_architecture}. Data on average device performance adapted from U.S. Department of Energy (DOE) Reports \cite{doe_ssl_multiyear_2007}\cite{doe_ssl_multiyear_2008}\cite{doe_ssl_multiyear_2013}\cite{doe_ssl_rnd_2016}\cite{doe_ssl_rnd_2018} and an Osram company report \cite{beale_leds_2015}.}
\label{fgr:subeff}
\vspace{-20mm}
\end{figure}

\clearpage
\suppnote{Non-Phosphor-Related LED Innovations}

\clearpage
\suppnote{Phosphor-Related LED Innovations}
\label{sec:innovation_phosphor}

\suppnote{Spectral Data for Phosphors}

\clearpage
\suppref{Full List of Sources for Figures}
\label{sec:sources}

\clearpage
\addcontentsline{toc}{section}{Supplementary Methods}

\suppmeth{Domain Definition}
\label{sec:domain}

\textit{Elsevier Scopus}\footnote{\url{https://www.scopus.com/search/}} advanced search query:

\begin{pseudocode}
TITLE-ABS-KEY(("light-emitting" OR "light emitting") W/2 diode*)
AND NOT
TITLE-ABS-KEY(solar OR violet OR laser)
AND NOT
TITLE-ABS-KEY(perovskite OR GaAsP OR AlGaInP OR GaAlAs OR ZnO)
AND NOT
TITLE-ABS-KEY(organic OR OLED* OR polymer*)
AND NOT
SUBJAREA(ARTS OR BUSI OR DECI OR ECON OR PSYC OR SOCI)
AND NOT
SUBJAREA(MEDI OR NURS OR VETE OR DENT OR HEAL OR MULT)
AND NOT
SUBJAREA(AGRI OR BIOC OR IMMU OR NEUR OR PHAR)
AND NOT
SUBJAREA(envi OR EART OR comp)
\end{pseudocode}

\suppmeth{Metrics for Quantifying Technological Progress in LEDs}

\textbf{Motivation for Metrics Selection}

@@

\clearpage
\suppmeth{Device Performance Metrics}
\label{sec:device_performance_metrics}

@@

\clearpage
\suppmeth{Consumer Experience Metrics}
\label{sec:metrics_consumer}

@@

\suppmeth{Background of Interviewed Experts}

\clearpage
\suppmeth{Cost Model Structure and Limitations}
\label{sec:costmodel_structure}

@@

@@

\suppmeth{Yielded Cost}
\label{sec:cost_computation}

@@

\suppmeth{Contribution of Variables}
\label{sec:contribution_variables}

@@

\addcontentsline{toc}{section}{Supplementary Discussion}

\suppdisc{Cost Model Sensitivity Analysis}

@@

\clearpage
\suppdisc{Cost Data Comparison with Industry Projections}
\label{sec:cost_model_calibration}

@@

\clearpage
\addcontentsline{toc}{section}{Supplementary References}
\printbibliography[title=Supplementary References]
